Possible Inconsistency in Maximum Likelihood Calculation of Ancestral States

### 2017-03-21 joint_inf.tex
Infrastructurizing and renaming.

Table~\ref{tab:sitepatprob} contains calculations of site pattern frequencies under these two topologies, calculated using the Hadamard transform approach outlined in 8.6 of Semple and Steel \cite{semplesteel}.
Table~\ref{tab:likelihoods} contains calculations of likelihood values for fixed site patterns and topologies, with the maximum values over ancestral state patterns noted.

@@

\bibliographystyle{plain}
\bibliography{sample}

>>>>

Table~\ref{tab:sitepatprob} contains calculations of site pattern frequencies under these two topologies, calculated using the Hadamard transform approach outlined in 8.6 of Semple and Steel \cite{Semple2003-em}.
Table~\ref{tab:likelihoods} contains calculations of likelihood values for fixed site patterns and topologies, with the maximum values over ancestral state patterns noted.

@@

\bibliographystyle{plain}
\bibliography{joint_inf}
